### 2018-07-30 Paper/intro.tex
...

\paragraph{Motivation}
Surrogate modeling has become a critical component of scientific computing
owing to the emergence of the field of uncertainty quantification for
scientific and engineering applications. Commonly used approaches for
surrogate modeling include polynomial chaos expansions
(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
regression splines (MARS)~\cite{friedman93}, Gaussian processes
(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}. A 
pertinent challenge associated with surrogate construction involves the
process of \textit{training} that typically requires a large number of model runs.
In situations involving large-dimensional systems,
and computationally intensive simulations, the training of a surrogate
becomes remarkably challenging and even prohibitive in some cases. A possible
approach for mitigating this challenge involves computation of sensitivity
measures (e.g. Sobol' indices~\cite{Sobol93,Sobol:2001,Owen13,SaltelliRattoAndresEtAl08})
to ascertain important parameters that predominantly contribute towards the variability
of the model output. Sensitivity-based dimension reduction could thus help
reduce the computational effort significantly. However, numerically estimating
the Sobol' indices that involve multi-dimensional integrals can be a demanding task
in itself. In fact, surrogate models are constructed to estimate the 
Sobol sensitivity indices for a variety of applications including in ocean 
modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
to name a few. Hence, this common practical issue in scientific computing can
be characterized as a ``chicken-and-egg" problem.

>>>>

%\paragraph{Motivation}
Computing statistical properties of 
complex systems containing uncertain parameters is
challening due to the need for a large number of expensive model evaluations. 
Surrogate models make such computations possible by replacing 
expensive model runs with cheap evaluations of an approximate model.
%
%Surrogate modeling has become a critical component of scientific computing
%owing to the emergence of the field of uncertainty quantification for
%scientific and engineering applications. 
%
Commonly used approaches for surrogate modeling include polynomial chaos
expansions (PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate
adaptive regression splines (MARS)~\cite{friedman93}, Gaussian processes
(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}. A pertinent
challenge associated with surrogate construction involves the process of
\textit{training} that typically requires a large number of model runs.  In
situations involving large-dimensional systems, and computationally intensive
simulations, the training of a surrogate becomes challenging and
even prohibitive in some cases. A possible approach for mitigating this
challenge involves computation of global sensitivity measures such as Sobol'
indices~\cite{Sobol93,Sobol:2001,Owen13,SaltelliRattoAndresEtAl08} to identify
the \emph{important parameters}---i.e., parameters that predominantly
contribute towards the variability of the model output.

Sensitivity-based
dimension reduction can help reduce the computational effort
significantly. However, numerically estimating the Sobol' indices, which
involve multi-dimensional integrals, can be a demanding task in itself. In
fact, often surrogate models are constructed to estimate the Sobol' sensitivity
indices; this has been done for a variety of applications including in ocean
modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014} to
name a few. 
We are thus, faced with a ``chicken-and-egg'' problem: on the one hand,
computing global sensitivity measures enable dimension reduction, which in turn
enable efficient surrogate model construction.  On the other hand, computing
sensitivity measures is expensive and is often made possible by using
surrogate models. Development of an approach for 
overcoming this chicken-and-egg problem is a major goal of this article.

%Hence, this common practical issue in scientific computing can
%be characterized as a ``chicken-and-egg" problem.
